A sheaf--function dictionary for algebraic tori over local fields

### 2013-08-17 shanghai.tex
Working on section 3

@@

  Since $a_i^* (\gqcs{L}\vert_{\bG^i})$ is a constant sheaf and since the pull-back
  of a constant sheaf (along $g_j$, in this case) is a constant sheaf,
  it follows that $b_j^* \left( (\bf^*\gqcs{L})\vert_{\bH^j}\right)$
  is a constant sheaf. Thus, $\bf^*\gqcs{L}$ is locally constant on
  $\bH^j$. Since $(\bf^*\gqcs{L})_{\bg} = \gqcs{L}_{f(\bg)}$ for every
  geometric point ${\bg}$ on $\bG$, and since $\gqcs{L}$ has
  rank $1$ on connected components of $\bG$, it follows that
  $f^*\gqcs{L}$ also has rank $1$ on connected components of $\bG$.
  This completes the proof that $\bf^*\gqcs{L}$ satisfies condition \ref{CS.0}.

  To see that $(\bfxf)^* \gqcs{L}$ satisfies
  condition \ref{CS.1} simply apply the functor $(\bfxf)^*$
  to \ref{CS.1} for $\qcs{L}$ and use the canonical isomorphism
  $(\bfxf)^*(\LxL) \iso \bf^*\gqcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gqcs{L}$
  (a few times). Likewise, to see that $\bf^*\gqcs{L}$ satisfies condition
  \ref{CS.2}, apply the same functor to \ref{CS.2} for $\gqcs{L}$.
  Then use the fact that $f$ is defined over $\Fq$, so
  $(\bfxf)^*\Frob{\GxxG}^* \iso \Frob{\GxxG}^* (\bfxf)^*$,
  and the fact that $f$ is a morphism of group schemes, so
  $(\bfxf)^* \bm^*\iso \bm^* \bf^*$
  (isomorphisms of functors on constructible sheaves).

  To see that $(\gqcs{L},\mu,\phi) \mapsto (\bf^*\gqcs{L},(\bfxf)^*\mu,\bf^*F)$
  defines a functor $f^* : \QC(G) \to \QC(H)$ one applies the functors $\bf^*$ and
  $\bf^*\tight{1}{\times}{1}\bf^*$ to \ref{CS.3} and argue as
  above. It follows from the fact that sheaf hom commutes with these
  functors that $f^* : \QC(G) \to \QC(H)$ is a monoidal functor.
%
  The fact that the functor $f^* : \QC(G) \to \QC(H)$ commutes with
  the trace of Frobenius, in the sense above, follows immediately from
  the definitions; see \cite{laumon:87a}*{1.1.1.2}, where the ambient
  hypothesis that $X$ is of finite type over $\Fq$ can be replaced by
  the hypothesis that $X$ is locally of finite type over $\Fq$.

  Finally, the fact that $(f\circ g)^* = g^* \circ f^*$ follows from the analogous
  statements about the pullbacks functor on $\ell$-adic constructible sheaves.
 % \David{Is this explanation of $(f\circ g)^* = g^* \circ f^*$ sufficient?}
\end{proof}

>>>>

\David{insert some commentary on this proposition: it will be very useful to us}

@@

  Since $a_i^* (\gqcs{L}\vert_{\bG^i})$ is a constant sheaf, its pullback
  $b_j^* \left( (\bf^*\gqcs{L})\vert_{\bH^j}\right)$ along $g_j$ is also constant.
  Thus $\bf^*\gqcs{L}$ is locally constant on
  $\bH^j$. Since $(\bf^*\gqcs{L})_{\bg} = \gqcs{L}_{f(\bg)}$ for every
  geometric point ${\bg}$ on $\bG$, and since $\gqcs{L}$ has
  rank $1$ on connected components of $\bG$, it follows that
  $f^*\gqcs{L}$ also has rank $1$ on connected components of $\bG$.
  This completes the proof that $\bf^*\gqcs{L}$ satisfies condition \ref{CS.0}.

  To see that $(\bfxf)^* \mu$ satisfies
  condition \ref{CS.1}, apply the functor $(\bfxf)^*$
  to \ref{CS.1} for $\qcs{L}$ and use the canonical isomorphism
  $(\bfxf)^*(\LxL) \iso \bf^*\gqcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gqcs{L}$.
  To show that $f^*\qcs{L}$ satisfies condition
  \ref{CS.2}, apply the same functor to \ref{CS.2} for $\qcs{L}$.
  The fact that $f$ is a morphism of group schemes defined over $\Fq$ then
  yields isomorphisms $(\bfxf)^*\Frob{\GxxG}^* \iso \Frob{\GxxG}^* (\bfxf)^*$
  and $(\bfxf)^* \bm^*\iso \bm^* \bf^*$ between functors of constructible sheaves.

  Applying $\bf^*$ and $\bf^* \tight{1}{\times}{1}\bf^*$ to \ref{CS.3} allows the application
  of $f^*$ to morphisms of quasicharacter sheaves; arguing as above shows that $f^*$ is
  a functor from $\QC(G)$ to $\QC(H)$.  Since tensor products commute with pullback
  $f^* : \QC(G) \to \QC(H)$ is a monoidal functor.
%
  The diagram relating $f^* : \QC(G) \to \QC(H)$, $f^* : G(k)^* \to H(k)^*$ and trace of Frobenius
  commutes by \cite{laumon:87a}*{1.1.1.2}, where the ambient
  hypothesis that $X$ is of finite type over $\Fq$ can be replaced by
  the hypothesis that $X$ is locally of finite type over $\Fq$.

  Finally, the fact that $(f\circ g)^* = g^* \circ f^*$ follows from the analogous
  statements about the pullback functor on $\ell$-adic constructible sheaves.
\end{proof}
